Katana: A Userland Toolchain-Oriented Hotpatching System

### 2010-06-21 doc/katana.tex
some fixes for licensing. Documentation is under GNU FDL

% Created 2010-06-15 Tue 22:01
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{soul}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{graphicx}

\title{Katana: A Userland Toolchain-Oriented Hotpatching System}
\author{James Oakley}
\date{15 June 2010}

@@

\begin{itemize}
\item Patch any major programs: it has not yet been demonstrated on
    anything more than toy examples
\item Provide any method to handle opaque data it cannot patch (void*,
    situations where which action a user would prefer is unclear, etc)
\item Patch previously patched processes
\item Provide robust operation
\item Run on any architectures other than x86 and x86-64
\item Tested on any operating system besides Linux
\item Allow for calls in patched code to previously unused functions
\item Work for programs which actually make use of some of the large
    code model features of the x86-64 ABI.
\item And much more
\end{itemize}
  See \hyperref[sec-10]{Roadmap} for more things which are not complete

@@

  This section is highly incomplete. Future goals include
\begin{itemize}
\item Better interaction with the heap and dynamically allocated variables
\item Better interaction with void*
\item More efficient use of .rodata
\item Patching already patched processes
\item Patch composition
\item Patch safety checking: make sure a patch actually corresponds to
    the process it's being applied to
\item Storing warnings from generation inside a patch
\end{itemize}

>>>>

% Created 2010-06-20 Sun 22:23
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{soul}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{graphicx}

\title{Katana: A Userland Toolchain-Oriented Hotpatching System}
\author{James Oakley}
\date{20 June 2010}

@@

\begin{itemize}
\item Patch any major programs: it has not yet been demonstrated on
    anything more than toy examples
\item Provide any method to handle opaque data it cannot patch (void*,
    situations where which action a user would prefer is unclear, etc)
\item Patch previously patched processes
\item Provide robust operation
\item Run on any architectures other than x86 and x86-64
\item Tested on any operating system besides GNU/Linux
\item Allow for calls in patched code to previously unused functions
\item Work for programs which actually make use of some of the large
    code model features of the x86-64 ABI.
\item And much more
\end{itemize}
  See \hyperref[sec-10]{Roadmap} for more things which are not complete

@@

  This section is highly incomplete. Future goals include
\begin{itemize}
\item Better interaction with the heap and dynamically allocated variables
\item Better interaction with void*
\item More efficient use of .rodata
\item Patching already patched processes
\item Patch composition
\item Patch safety checking: make sure a patch actually corresponds to
    the process it's being applied to
\item Storing warnings from generation inside a patch
\end{itemize}
\section{Credits and Licensing}
\label{sec-11}

  Katana is under development at Dartmouth College and Copyright 2010
  Dartmouth College. It may be distributed under the terms of the GNU
  General Public License with attribution to Dartmouth College as
  specified in the file COPYING distributed with Katana. This document
  is Copyright 2010 Dartmouth College and may be distributed under the
  terms of the GNU Free Documentation License

  Katana is being written by James Oakley and was designed
  by Sergey Bratus, Ashwin Ramaswamy, James Oakley, Michael Locasto,
  and Sean Smith.
